### 2017-03-27 paper/evaluation.tex
reworked rq3

\newcommand{\RQA}{How prevalent is the occurence of time-consuming
  regression test suites in open-source projects?}
\newcommand{\RQB}{How the time cost is distributed across test cases?}
\newcommand{\RQC}{How often parallelization settings appear in build
  files?}
\newcommand{\RQD}{What is the impact of parallelization?}
%%\newcommand{\RQE}{What factors contribute to improve performance
%%  through parallelization?\Jbc{Previously as "When does
%%    parallelization works and when it does not so great?"}}
\newcommand{\RQF}{What are the limitations of low-level parallelism?}

@@

To evaluate the presence of parallelization settings (see Section
\ref{sec:modes}), we considered all projects classified as \medg{} and
\longg{}-running, a total of \numMedLong{} subjects (see
Figure~\ref{fig:rq1-barplot}). To reduce noise we did not consider
projects with \shortg{}-running test suites as we observed that
\percentShortSequential{} of those projects do not use parallelism;
including them would favor sequential execution in our analysis.

To answer \numRQC{} we initially mined build files (\ie, \pomf{}) that
contain parallelization keywords, namely \CodeIn{forkMode},
\CodeIn{forkCount}, and \CodeIn{parallel}.  According to the Maven
surefire documentation\Fix{cite surefire doc}, any configuration to
run tests in parallel must contain one of these keywords. This mining
step, however, is not sound as a matching project may not indicate a
project with a valid configuration for running tests in parallel.
False positive can happen because of comments, for instance.  
To eliminate the cases of false positives and also to categorize true
positive cases, we complemented the initial mining step with a manual
inspection of files.

@@

\subsubsection{Distribution of parallel modes}

From the \numProjectsPar{} projects identified above, we investigated
further the \numPomMatchedValid{} build files with parallel settings.
We analyzed the support and distribution of parallel modes from this
subset of projects. To calculate the distribution of parallel modes,
we considered only the presence of the mode in at least one of the
project settings.  Recall that a build file may contain more than one
parallel setting and a project may contain several sub-modules with
build files.  In case the value of a parallel option is resolved
dynamically (\eg, via command-line argument or system variable) we
compute all modes related to the option. For instance, depending on
the value, the \CodeIn{parallel} option can be \Seq{} (\CodeIn{none}),
\ParClassSeqMeth{} (\CodeIn{classes}), \SeqClassParMeth{},
(\CodeIn{methods}), and \ParClassParMeth{} (\CodeIn{all}).
Figure~\ref{fig:freqmodes} summarizes our findings. \Jbc{Given that we
checked each configuration, we could elaborate how these settings are
used.} \Fix{Missing conclusion: Fork the most used configuration}

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.32\textwidth]{plots/parallel-modes.pdf}
    \caption{\label{fig:freqmodes}Distribution of parallel modes
    identified in a subset of \numProjectsPar{} projects (unused modes
    omitted). A single project may have support to more than one
    parallel mode.}
\end{figure}

@@

\Fix{---------------------}

>>>>

\newcommand{\RQA}{How prevalent is the occurence of time-consuming
  regression test suites in open-source projects?}
\newcommand{\RQB}{How the time cost is distributed across test cases?}
\newcommand{\RQC}{How often developers add support to parallel
execution of test suites?}
\newcommand{\RQD}{What is the impact of parallelization?}
%%\newcommand{\RQE}{What factors contribute to improve performance
%%  through parallelization?\Jbc{Previously as "When does
%%    parallelization works and when it does not so great?"}}
\newcommand{\RQF}{What are the limitations of low-level parallelism?}

@@

To evaluate the support of parallelization in test suites, we
considered all projects classified as \medg{} and \longg{}-running, a
total of \numMedLong{} subjects (see Figure~\ref{fig:rq1-barplot}). To
reduce noise we did not consider projects with \shortg{}-running test
suites as we observed that \percentShortSequential{} of those projects
do not use parallelism; including them would favor sequential
execution in our analysis.

To answer \numRQC{} we initially configured Maven to output
configuration settings and re-executed the tests to collect and
classify the test suites according to its level of parallelization
(see Section \ref{sec:modes}).  The rationale is that if a test suite
is configured to run in parallel, Maven is going to display the
configuration and we can classify it according to its parallelization
level.  We are interested to know how frequent are parallel executions
and what configurations are more popular.  According to Maven's
documentation\Fix{cite surefire doc}, the set of parameters to run
tests in parallel is described as follows: \CodeIn{parallel} defines
the parallelism granularity within a JVM (\eg, methods or classes);
\CodeIn{threadCounter} defines the size of the thread pool; and
\CodeIn{forkCount} defines the number of forked JVMs. Additional
options exists and depends on theses parameters to take effect. To
avoid waiting all tests to terminate, we just run the bootstrap phase
and we skip the actual test execution. \Jbc{Missing: explain how we
mapped the configurations to parallel level.}
Figure~\ref{fig:freqmodes-dynamic} summarizes our findings.

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.32\textwidth]{plots/barplot-modes-dynamic.pdf}
    \caption{\label{fig:freqmodes-dynamic}Distribution of parallel modes 
    identified dynamically in a subset of \numProjectsPar{} projects.
    A project may have support to more than one parallel mode. Also,
    a project may run only a subset tests in parallel by default.}
\end{figure}

\Fix{Elaborate findings....}

\subsubsection{Support of parallelization configuration in build files}

We complemented our previous investigation with a static analysis of
several \pomf{} files from the \numMedLong{} subjects. The rationale
is that some projects might not enable parallelism in the default
execution. \Jbc{Remember to explain that we need the previous analysis
because some configurations are unreachable statically when inherited
from some external module}.

%% To answer \numRQC{} we initially mined build files (\ie, \pomf{}) .
%% must contain one of these keywords that
%% contain parallelization keywords, namely \CodeIn{forkMode},
%% \CodeIn{forkCount}, and \CodeIn{parallel}.

This mining step, however, is not sound as a matching project may not
indicate a project with a valid configuration for running tests in
parallel.  False positive can happen because of comments, for
instance.  To eliminate the cases of false positives and also to
categorize true positive cases, we complemented the initial mining
step with a manual inspection of files.

@@

From the \numProjectsPar{} projects identified above, we investigated
further the \numPomMatchedValid{} build files with parallel settings.
We analyzed the support and distribution of parallel modes from this
subset of projects. To calculate the distribution of parallel modes,
we considered only the presence of the mode in at least one of the
project settings.  Recall that a build file may contain more than one
parallel setting and a project may contain several sub-modules with
build files.  In case the value of a parallel option is resolved
dynamically (\eg, via command-line argument or system variable) we
compute all modes related to the option. For instance, depending on
the value, the \CodeIn{parallel} option can be \Seq{} (\CodeIn{none}),
\ParClassSeqMeth{} (\CodeIn{classes}), \SeqClassParMeth{},
(\CodeIn{methods}), and \ParClassParMeth{} (\CodeIn{all}).
Figure~\ref{fig:freqmodes-static} summarizes our findings. \Jbc{Given that we
checked each configuration, we could elaborate how these settings are
used.} \Fix{Missing conclusion: Fork the most used configuration}

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.32\textwidth]{plots/barplot-modes-static.pdf}
    \caption{\label{fig:freqmodes-static}Distribution of parallel modes 
    identified statically in a subset of \numProjectsPar{} projects.
    A project may have support to more than one parallel mode.}
\end{figure}

\begin{center}
\fbox{
  \begin{minipage}{8cm}
      \textit{Answering \numRQC{}:}~\emph{Overall, results indicate
      that \Jbc{summarize results from both parts (static and
      dynamic)}.} 
  \end{minipage}
}
\end{center}

@@

\begin{center}
\fbox{
  \begin{minipage}{8cm}
      \textit{Answering \numRQD{}:}~\emph{\Jbc{summarize
      findings.....}}
  \end{minipage}
}
\end{center}
